\huge A Usability Evaluation of Tor Launcher

### 2017-03-15 pets2017-paper/pets2017-paper.tex
More about norcie2012eliminating.

\section{Related Work}
\label{sec:related} 
Previous usability studies on Tor have focused on installation and use, but not on setting up Tor Browser. Norcie et~al.~\cite{norcie2012eliminating} observed 25 users and found that 64\% had issues that prevented them from installing or using Tor Browser. Fabian et~al.~\cite{fabian2010privately} revealed how users are frustrated by latency in Tor Browser enough not to use it, even if that latency benefits their anonymity~\cite{dingledine2009performance}. Clark et~al.~\cite{clark2007usability} evaluated various Tor Browser deployment options (Vidalia, Privoxy, Torbutton, and FoxyProxy--none of which are around today) to find that none were satisfactory from a usability perspective and offered advice on how to improve them. We do not know of any published usability evaluations of Tor Browser since the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}. Lee and Fifield~\cite{uxsprint} ran an informal UX sprint~\cite{uxsprint2015-tickets}.

>>>>

\section{Related Work}
\label{sec:related}

We do not know of any published usability studies of Tor Browser
since the introduction of Tor Launcher,
which happened in the 3.5 release in December 2013~\cite{torbrowser-35}.
There are some earlier usability studies that focused on installation and use,
but not on setting up Tor Browser.
Norcie et~al.~\cite{norcie2012eliminating}, in 2012,
investigated ``stop-points''
in the installation and use of Tor Browser,
places where users' uncertainty about what to do
put them at risk of not completing a task.
Of their 25 participants, 64\% encountered at least one stop-point,
such as a long startup time, misidentified icons, or confusion with other web browsers.
Fabian et~al.~\cite{fabian2010privately} revealed how users are frustrated by latency in Tor Browser enough not to use it, even if that latency benefits their anonymity~\cite{dingledine2009performance}. Clark et~al.~\cite{clark2007usability} evaluated various Tor Browser deployment options (Vidalia, Privoxy, Torbutton, and FoxyProxy--none of which are around today) to find that none were satisfactory from a usability perspective and offered advice on how to improve them.
Lee and Fifield~\cite{uxsprint} ran an informal UX sprint~\cite{uxsprint2015-tickets}.
